msc dissertation

### 2021-08-05 msc dissertation code.Rmd
latest

pennycook1 <- read_csv("Pennycook et al._Study 1.csv")
pennycook2 <- read_csv("Pennycook et al._Study 2.csv")
# Quick check
head(pennycook2)

@@

###find out the number of participants for each attention check
attention1 <- subset(pennystudy2r1, dummycheck %in% c("1","2","3"))
attention2 <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
attention3 <- subset(pennystudy2r1, dummycheck %in% c("3"))
```

@@

>>>>

pennycook2 <- read_csv("Pennycook et al._Study 2.csv")
# Quick check
head(pennycook2)

@@

###find out the number of participants (obs) for each attention check level
attention1 <- subset(pennystudy2r1, dummycheck %in% c("1","2","3"))
attention2 <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
attention3 <- subset(pennystudy2r1, dummycheck %in% c("3"))
```

@@

## use glm, stepwise approach to see how each factor explaining the sharing intention. The family for the model is binomial since the dependent variable is dichotomous.
glm0 <- glm(measurement ~ 1, data = pennys2r1long_nona, family = binomial(link = "logit"))

glm1 <- glm(measurement ~ condition, data = pennys2r1long_nona, family = binomial(link = "logit"))

glm2 <- glm(measurement ~ condition + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))

glm3 <- glm(measurement ~ condition + attentioncheck + headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))

glm4 <- glm(measurement ~ condition + attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))

anova(glm0,glm1,glm2,glm3,glm4,test='LR')

##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
summary(glm6)

glm5 <- glm(measurement ~ attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
glm6 <- glm(measurement ~ headlineveracity + attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))

summary(glm7)

##maybe a mixed effect models?
#create a new column that recode item number from fake to real to 1-30, with 1-15 indicate fake, 16-30 indicate real

pennys2r1long <- within(pennys2r1long,{
  item_id <- NA
  item_id[newstype == "Fake1_1"] <- 1
  item_id[newstype == "Fake1_2"] <- 2
  item_id[newstype == "Fake1_3"] <- 3
  item_id[newstype == "Fake1_4"] <- 4
  item_id[newstype == "Fake1_5"] <- 5
  item_id[newstype == "Fake1_6"] <- 6
  item_id[newstype == "Fake1_7"] <- 7
  item_id[newstype == "Fake1_8"] <- 8
  item_id[newstype == "Fake1_9"] <- 9
  item_id[newstype == "Fake1_10"] <- 10
  item_id[newstype == "Fake1_11"] <- 11
  item_id[newstype == "Fake1_12"] <- 12
  item_id[newstype == "Fake1_13"] <- 13
  item_id[newstype == "Fake1_14"] <- 14
  item_id[newstype == "Fake1_15"] <- 15
  item_id[newstype == "Real1_1"] <- 16
  item_id[newstype == "Real1_2"] <- 17
  item_id[newstype == "Real1_3"] <- 18
  item_id[newstype == "Real1_4"] <- 19
  item_id[newstype == "Real1_5"] <- 20
  item_id[newstype == "Real1_6"] <- 21
  item_id[newstype == "Real1_7"] <- 22
  item_id[newstype == "Real1_8"] <- 23
  item_id[newstype == "Real1_9"] <- 24
  item_id[newstype == "Real1_10"] <- 25
  item_id[newstype == "Real1_11"] <- 26
  item_id[newstype == "Real1_12"] <- 27
  item_id[newstype == "Real1_13"] <- 28
  item_id[newstype == "Real1_14"] <- 29
  item_id[newstype == "Real1_15"] <- 30
})

library(lme4) 
library(lmerTest)

#model 1, item_id indicates repeated measurements for each item
mult1 <- lmer (measurement ~ condition + attentioncheck + headlineveracity + (1|item_id),
             data = pennys2r1long)
summary(mult1)
